### 2003-12-04 Documentation/part1.tex
*** empty log message ***

\bi
\item
 Single- and multiple experiment support
\item 
Example: Finding degenerate solutions with multiple experiments!?
\item
 What does that do?
\item
 Example: how to treat sign-degeneracy in th13-limit
\ei

>>>>

\example{Finding the $\mathrm{sgn}(\ldm)$-degeneracy}{
\label{ex:sgndeg}

In many cases, one can find the $\mathrm{sgn}(\ldm)$-degeneracy with {\tt ChiAll}: One lets the local minimizer start at the position of the suspected solution at the opposite sign of $\ldm$.  The following example corresponds to finding the degenerate solution for the example on page~\pageref{ex:corrth13dcp}.
\begin{quote}
{\tt
{\footnotesize
/\% Experiment initialization: \%/ \\
ClearExp(); InitExperiment("{\tt NuFact2.exp}"); SetRunningTime(0,4.0); \\
\\
/\% Set reference rate vector: \%/ \\
th12=arcsin(sqrt(0.8))/2; sdm=7e-5; th23=3.14/4; ldm=2e-3; \\
th13=arcsin(sqrt(0.001))/2; dcp=3.14/2; \\
\mbox{SetVacuumParameters(\{th12, \, th13, \, th23, \, dcp, \, sdm, \, ldm\});  SetRates();} \\
\\
/\% Find negative-sign solution: \%/ \\
SetStartingValues(\{th12, \, th13, \, th23, \, dcp, \, sdm, \, -ldm, \, 1.0\}); \\
SetInputErrors(\{th12*0.1, \, 10, \, 10, \, 10, \, sdm*0.1, \, ldm/3, \, 0.05\}); \\
d = ChiAll(\{th12, \, th13, \, th23, \, dcp, \, sdm, \, ldm, \, 1.0\}); \\
\\
/\% Compute chi-square matrix: \%/ \\
for (float x=-4; x<-2; x=x+2/50) \\
\hspace*{0.5cm} for (float y=0; y<200; y=y+200/50) \{ \\
\hspace*{1cm} theth13 = arcsin(sqrt(10$\hat{\, \, \,}$x))/2; \\
\mbox{\hspace*{1cm} Print(\{x,y,Chi(\{d[2], theth13,  d[4],  y, d[6], d[7], d[8]\}) \}) \};}
}
}
\end{quote}

The resulting matrix can then be plotted as a contour plot in addition to the original solution (2 d.o.f., gray contours):
\begin{center}
\colorbox{white}{\includegraphics[width=7.5cm]{correntex}}
\end{center}

}
\bi
\item
 Single- and multiple experiment support
\item 
Example: Finding degenerate solutions with multiple experiments!?
\item
 What does that do?
\item
 Example: how to treat sign-degeneracy in th13-limit
\ei
